Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2016-08-08 paper/letter.tex
+1 paragraph on the rotation model

The rotation model corresponds to the work presented in
\cite{GaravitoCamargo2014}. 
In that model the Ly-$\alpha$ photons are propagated 
within a spherical and homogeneous cloud of HI gas undergoing solid
body rotation.
The sphere is fully characterized by three parameters: the optical
depth $\tau$ measured from the center to the surface, the HI
temperature, $T$, and the velocity at the surface $V_{\rm max}$.  
Photons are emitted at their natural frequency from the center of the
sphere. 
Including the effect of dust only changes the overall line
normalization but not its shape.  
The results we report in the main body of the paper do not include any
dust model.
In the current work, the radiative transfer simulations were done
using Monte Carlo simulations with the code \texttt{CLARA}
\cite{CLARA}.

The main effects of rotation are the following.
First, rotation breaks spherical symmetry of the
static case, making the line's observed morphology dependent on the
angle between the line-of-sight and the rotation axis.

First, the line width increases with rotational velocity.
Second, the intensity at the line's center alto 
In this model rotation increases the width of the line and the flux at
the line center. 
Furthermore, observers at different line of sights
(LOS) angles with respect to the rotation axis of the galaxy will observe
different morphologies of the line. LOS parallel to the rotation axis
will tend to observe a double peaked line, while an observer with a LOS
perpendicular to the rotation axis will observed a single peaked
broader line.

>>>>

The rotation model corresponds to the work presented in
\cite{GaravitoCamargo2014}. 
In that model the Ly-$\alpha$ photons are propagated 
within a spherical and homogeneous cloud of HI gas undergoing solid
body rotation.
The sphere is fully characterized by three parameters: the optical
depth $\tau$ measured from the center to its surface, the HI
temperature $T$, and the linear surface velocity $V_{\rm max}$.  
Photons are emitted at their natural frequency from the center of the
sphere. 
Including the effect of dust only changes the overall line
normalization but not its shape.  
The results we report in the main body of the paper do not include any
dust model.
In the current work, the radiative transfer simulations were done
using Monte Carlo simulations with the code \texttt{CLARA}
\cite{CLARA}.

The first important effect of rotation is that it breaks the spherical
symmetry of the static case. 
Now the line's observed morphology depends on the angle between the
line-of-sight (LOS) and the rotation axis. 
LOS parallel to the rotation axis tend to observed the line without
any modification from rotation, while the perpendicular LOS will
observe a maximal change in the line's morphology due to rotation.

The main change in the line's morphology is that it broadens and the
intensity at the center increases. 
For high enough rotational velocities the intensity at the peak's
center increases so much that the line goes from double to single
peaked, sometimes slightly triple peaked.
This is the feature that allows this model to fit the observational
features of \tol.

There is a concise analytical description for those features.
This description takes into account how different parts of the
sphere's surface shift in frequency the \lya photons. 
Different shifts in frequency come from different values for the projected
velocity along the LOS. 
As presented in \cite{CLARA}, using the analytical solution for the
\lya sphectra of a static sphere plus the right frequency shifts
computed from geometrical considerations, one is able to produce an
analytical solution for the rotating sphere that reproduces the main
features found with the full numerical simulation.
